Predicting tree failure likelihood for utility risk mitigation via artificial intelligence

### 2021-03-04 docs/manuscript/manuscript.tex
Replace monospace with proper notation

In \autoref{tab:scenarios}, the first scenario considered each likelihood of failure category separately, as an arborist would do in practice. The second scenario considered only the highest and lowest likelihood of failure categories used in the study to clearly distinguish between categories. Since Previous research has suggested that professionals more often disagree when distinguishing between possible and probable likelihood of failure (KOESER), in the third scenario, we pooled trees in the probable and possible categories and compared them to trees in the improbable category. In the fourth scenario, we pooled trees in the possible and improbable categories and compared them to trees in the probable scenario. In practice, this scenario is less likely because arborists typically distinguish trees with an improbable likelihood of failure as those with minimal or no structural defects. It requires additional judgment to distinguish trees with probable or possible likelihood of failure because an arborist must assess the severity of structural defects, the presence of response growth, and the expected loads \cite{smiley2017best}.

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{l l c}\toprule
    \bf Symbol            & \bf Definition  \\\midrule
    $i$     &  \ Given observation \\
    $c$          & \ Class\\
    $s_c$        & \ Class-specified score \\
    $\hat y_i$       & \ Predicted class of a given observation \\
    $y_i$        & \ Observed (true) class of a given observation \\
    $f(s_c)$        & \ Softmax activation function \\
    $p_{i,c}$        & \ Predicted probability that the i\textsuperscript{th} observation belongs to class c \\
    $L^{CE}_i$        & \ Categorical cross entropy loss function of a single observation \\
    $Pr$ & \ Precision \\
    $Re$ & \ Recall \\
    $F_1$ & \ F_1 score \\\bottomrule
    \end{tabular}
    \caption{Symbols description}
    \label{tab:symbols}
\end{table}

>>>>

In \autoref{tab:scenarios}, the first scenario considered each likelihood of failure category separately, as an arborist would do in practice. The second scenario considered only the highest and lowest likelihood of failure categories used in the study to clearly distinguish between categories. Since Previous research has suggested that professionals more often disagree when distinguishing between possible and probable likelihood of failure \cite{koeser2020can}, in the third scenario, we pooled trees in the probable and possible categories and compared them to trees in the improbable category. In the fourth scenario, we pooled trees in the possible and improbable categories and compared them to trees in the probable scenario. In practice, this scenario is less likely because arborists typically distinguish trees with an improbable likelihood of failure as those with minimal or no structural defects. It requires additional judgment to distinguish trees with probable or possible likelihood of failure because an arborist must assess the severity of structural defects, the presence of response growth, and the expected loads \cite{smiley2017best}.

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{l l c}\toprule
    \bf Symbol            & \bf Definition  \\\midrule
    $i$     &  \ Given observation \\
    $c$          & \ Class\\
    $s_c$        & \ Class-specified score \\
    $\hat y_i$       & \ Predicted class of a given observation \\
    $y_i$        & \ Observed (true) class of a given observation \\
    $f(s_c)$        & \ Softmax activation function \\
    $p_{i,c}$        & \ Predicted probability that the i\textsuperscript{th} observation belongs to class c \\
    $L^{CE}_i$        & \ Categorical cross entropy loss function of a single observation \\
    $Pr$ & \ Precision \\
    $Re$ & \ Recall \\
    $F_1$ & \ $F_1$ score \\\bottomrule
    \end{tabular}
    \caption{Symbols description}
    \label{tab:symbols}
\end{table}
